\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-22 paper.tex
externalised Tikz node styling

@@

\tikzset{
  resource/.style={
    rectangle,
    minimum width=1cm,
    minimum height=8mm,
    thick, draw=black,
    top color=white,
    font=\ttfamily
  },
  representation/.style={
    rectangle, rounded corners=3mm,
    minimum width=2cm,
    minimum height=8mm,
    thick, draw=black,
    top color=white,
    font=\itshape
  }
}

@@

  \draw [->] (dsl) -> (sm)   node [midway,above=10pt]              {parse};
  \draw [->] (sm)  -> (cm)   node [midway,above=10pt,align=center] {semantic\\transform};
  \draw [->] (cm)  -> (code) node [midway,above=10pt]              {emit code};

  \draw [rounded corners,->]
        ($ (sm.east) - (5mm,4.5mm) $)
        -- ++(0,-.5)
        -| ($ (sm.west) + (5mm,-4.5mm) $)
           node [near start, below=1pt] {type inference};

  \draw [rounded corners,->]
        ($ (cm.east) - (5mm,4.5mm) $)
        -- ++(0,-.5)
        -| ($ (cm.west) + (5mm,-4.5mm) $)
           node [near start, below=1pt,align=center] {syntactic\\transform};

@@

\tikzset{
  class/.style={
    rectangle,
    minimum size=1cm,
    thick, draw=black,
    text centered,
    text width=1.75cm,
  },
  subclass/.style={thick,draw=black,>=open triangle 60,<-},
  aggregate/.style={thick,draw=black,>=open diamond,<-},
  composite/.style={thick,draw=black,>=diamond,<-},
  dependency/.style={thick,>=latex,->}
}

>>>>

\include{tikz}

@@

@@

  \draw [->] (dsl) -> (sm)   node [midway,above=15pt]              {parse};
  \draw [->] (sm)  -> (cm)   node [midway,above=15pt,align=center] {semantic\\transform};
  \draw [->] (cm)  -> (code) node [midway,above=15pt]              {emit code};

  \draw [rounded corners,->]
        ($ (sm.east) - (5mm,5mm) $)
        -- ++(0,-.5)
        -| ($ (sm.west) + (5mm,-5mm) $)
           node [near start, below=1pt] {type inference};

  \draw [rounded corners,->]
        ($ (cm.east) - (5mm,5mm) $)
        -- ++(0,-.5)
        -| ($ (cm.west) + (5mm,-5mm) $)
           node [near start, below=1pt,align=center] {syntactic\\transform};

@@
